---
title: "Project_2"
author: "Chris Lin"
date: "2/26/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Read in dataset, order by q-value, then create table with top 10 genes
```{r 1}
ds <- read.table('gene_exp.diff', header = TRUE, stringsAsFactors = FALSE)
ds <- ds[order(ds[,13] ),]
table <- ds[1:10,]
table_vals <- c('gene', 'value_1', 'log2.fold_change.', 'p_value', 'q_value') 
table <- table[table_vals]
table
```


#create histogram of log fold change with all genes
```{r 2}
hist <- hist(ds$log2.fold_change., breaks = 50)
```
#create dataset of log fold change with only significant genes
```{r 3}
ds1 <- subset(ds, ds$significant == 'yes')
```

#create histogram of log fold change with only significant genes

```{r 4}
hist1 <- hist(ds1$log2.fold_change., breaks = 50)
```
#subset significant genes for those with positive and negative log fold changes
```{r 5}
ds_up <- subset(ds, ds$log2.fold_change. > 0)
ds_down <- subset(ds, ds$log2.fold_change. < 0)
dim(ds_up)
dim(ds_down)
```
#write out up and down regulated genes to csv and txt files

```{r 6}
up_genes <- matrix(ds_up$gene)
down_genes <- matrix(ds_down$gene)

write.table(up_genes, "up_genes.csv", row.names = FALSE, col.names=FALSE, quote = FALSE)
write.table(up_genes, "down_genes.csv", row.names = FALSE, col.names=FALSE, quote = FALSE)
write.table(up_genes, "up_genes.txt", row.names = FALSE, col.names=FALSE, quote = FALSE)
write.table(up_genes, "down_genes.txt", row.names = FALSE, col.names=FALSE, quote = FALSE)
```
